\documentclass{resume} % Use the custom resume.cls style
\usepackage{afterpage}
\usepackage[left=0.5in,top=0.3in,right=0.5in,bottom=0.3in]{geometry} % Document margins
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{graphicx}


\setlist{nolistsep, topsep=-10pt,  leftmargin=0pt}
\setlength{\extrarowheight}{3pt}

\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1.1\baselineskip}{\baselineskip}
\titlespacing*{\subsection}{0pt}{0ex}{-2ex}


\name{Girish Mohan} % Your name
\address{~$+$~49~176~47372783 \\ girish\_mohan@live.com \\ \href{https://www.linkedin.com/in/giri91/}{LinkedIn}} % Your phone number and email
%\address{Voice AI Consultant \\ AI Automation Consultant} % Your role
\begin{document}

	%----------------------------------------------------------------------------------------
	%	Overview SECTION
	%----------------------------------------------------------------------------------------

	\begin{rSection}{Professional Summary}
		Consultant with hands-on experience designing, implementing, and operationalising voice \& chat-based AI solutions across customer service, lead qualification, appointment setting, \& sales discovery use cases. Combines end-to-end delivery experience - from requirements analysis, conversation design, NLU/prompt architecture, integration design, testing, rollout, \& continuous optimisation - with a structured engineering background in safety-critical autonomous vehicle programs.
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	TECHNICAL STRENGTHS SECTION
	%----------------------------------------------------------------------------------------

	\begin{rSection}{Technical Skills}
		\begin{itemize}
			\fontsize{10pt}{12pt}\selectfont
			\item \textbf{Conversational AI \& Customer Service} - Conversation design, voice/chat agent architecture, NLU intent mapping, dialogue flows, escalation design, objection handling, human handover, post-call logging.
			\item \textbf{AI Platforms \& Agent Tooling} - Vapi, LLM-based agents, prompt architecture, guardrails, Token Management
			\item \textbf{Automation \& Integration} - n8n, Claude Code, REST APIs, webhooks, CRM integration, calendar booking, email automation, Google Workspace APIs, Twilio.
			\item \textbf{Consulting \& Delivery} - Requirements analysis, stakeholder workshops, operating model design, rollout planning, incident/change handling, documentation, test strategy.
			\item \textbf{Engineering Governance} - ISO 26262, SOTIF, ASPICE, requirements-based testing, traceability, V\&V frameworks.
		\end{itemize}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	PROFESSIONAL EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------

	\begin{rSection}{Professional Experience}
		\vspace{2mm}
		\begin{rSubsection}{Avya Labs}{Jan 2026 - Present}{Independent AI Consultant}{Kornwestheim, DE}
			\fontsize{10pt}{12pt}\selectfont
		%	\item Deployed AI voice agents for businesses, with one agent live in production at Avya Labs.
			\item Designed \& deployed voice-agents for business use cases, including one internal agent handling lead qualification, appointment booking, CRM lookup, and email follow-up workflows.
			\item Defined operating model components for conversational AI agents including escalation logic, human handover, incident logging, post-call review, and continuous improvement loops.
			\item Designed integration architectures connecting agent front ends with CRM, scheduling, email, and reporting systems; translated business workflows into deterministic backend automations and measurable service outcomes.
%			\item \textbf{Hospital Appointment Setting Agent}: inbound agent handling scheduling, call routing and triage.
%			\item \textbf{Lead Qualification Agents} automated inbound lead triage, intent detection, CRM write-back - qualified lead routing and interaction logging for reviews.
			%\item Designed \textbf{agent systems} to keep AI decision-making separate from backend execution - ensuring reliable, predictable tool and API behaviour across multi-step workflows.
			%\item Agent integration with Google suits and calendar systems; built GDPR-compliant production website and AI-gated CI/CD pipeline.
		\end{rSubsection}

		\begin{rSubsection}{HOLON GmbH}{Jul 2025 - Dec 2025}{E/E Test Strategy Engineer}{Munich, DE}
			\fontsize{10pt}{12pt}\selectfont
%			\item Defined and implemented test strategies across test levels for the Holon People Mover autonomous vehicle platform.
            \item Defined cross-domain verification strategies for an autonomous mobility platform, aligning system requirements, supplier deliveries, test levels, and acceptance criteria across complex stakeholder groups.
			\item Identified and addressed process gaps to improve testing efficiency and cross-team consistency across software and hardware integration layers.
		\end{rSubsection}

		\begin{rSubsection}{Torc Europe GmbH}{Sep 2022 - Mar 2025}{Systems Engineer - Test Strategy}{Stuttgart, DE}
			\fontsize{10pt}{12pt}\selectfont
			%\item Led strategic test development and V\&V framework design for SAE L4 autonomous trucks.
			\item Led V\&V strategy development for autonomous truck software across test platforms, coordinating with requirements, sw, safety, \& leadership stakeholders.
			\item Implemented industry-standard  frameworks to enable engineering teams to adopt scalable testing methodologies.
		\end{rSubsection}

		\begin{rSubsection}{T\&S Engineering GmbH}{Sep 2018 - May 2022}{Consultant - System Test Engineer (Client: Robert Bosch GmbH)}{Stuttgart, DE}
			\fontsize{10pt}{12pt}\selectfont
			\item Designed and executed requirements-based test cases; managed defect tracking \& produced test coverage reports.
		\end{rSubsection}
		
%\begin{rSubsection}{Infosys Limited, \normalfont\textit{Mysore India, Sr. Sys Engineer - Process Automation}}{Apr 2013 - Aug 2016}{}{}
%	\item[] \vspace{-\itemsep}\vspace{-\parsep}\vspace{-\baselineskip}
%\end{rSubsection}

\begin{rSubsection}{Infosys Limited}{Apr 2013 - Aug 2016}{Senior Systems Engineer - Process Automation}{India}
	\item[] \vspace{-\baselineskip}
\end{rSubsection}

	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------

	\begin{rSection}{Education}
		{\bf Universit\'e d'Orl\'eans, France \& ISAT Nevers, France} \hfill {2018} \\ 
		{\small \emph{Joint Degree M.S. Automotive Engineering for Sustainable Mobility}} \\
		{\bf Mahatma Gandhi University, Kerala, India} \hfill {2012} \\ 
		{\small \emph{B.Tech. Automobile Engineering}}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%  Language  SECTION
	%----------------------------------------------------------------------------------------

	\begin{rSection}{Languages}
		English - C1  \quad $\diamond$ \quad German - B2  \quad $\diamond$ \quad French - B2 \quad $\diamond$ \quad Malayalam - Native \\\
	\end{rSection}

	%----------------------------------------------------------------------------------------
\end{document}
